My thesis

### 2020-02-04 manuscript/drafts/manuscript.Rmd
added definitions on model parameters - model (naive bayes) - feature selection - query strategy

---
title: "parameters"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: pdf_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

- number of training data (included/excluded)
- a model
- a query strategy
- a balance strategy (fixed)
- feature extraction

@@

@@

>>>>

---
title: "parameters"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: pdf_document
bibliography: asreview.bib
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

- a model
- a query strategy
- a balance strategy (fixed)
- a feature extraction strategy
- number of training data

The goal: 
Use these inputs to predict relevance of papers.

Numerical representation of texts
To perform a learning algorithm on the abstract, the content of the abstracts needs to be represented numerical.
To perform learning algorithms on the abstracts, their content has to be represented in a numerical way. 
This is done by transforming the textual content of the abstracts into numerical feature vectors. 
A classical example representation of texts is by 'bag of words' features, where for each text the number of occurrences of each word is stored. This leads to n features, where n is the number of distinct words in the texts. [@scikit-learn]

ASReview implements several feature extraction strategies. The following will be compared:

* Doc2Vec [@Le2014]
* Tfidf 
* SBERT
* embeddingIdf

The model is typically a learning algorithm used to predict the relevance of text.
The following models will be compared:

* Naive Bayes 
* Random Forests
* Support Vector Machine 
* Logistic Regression 
* **Dense Neural Network**

Active learning = 
increasing classification performance with every query. 
The query strategy determines the way unlabeled papers are queried to the researcher.

[@modAL2018]

The balance strategy

@@

## Models 
### Naive Bayes 
Naive Bayes assumes all features are independent given the class value. [@Zhang2004]

ASReview uses the ` MultinomialNB` from the scikit-learn package [@scikit-learn], that implements the naive Bayes algorithm for multinomially distributed data. 
` nb`

Hyperparameters
  * alpha - accounts for features not present in learning samples and prevents zero probabilities in further computations. ?

### Random Forests

### Support Vector Machine

### Logistic Regression

### *Dense Neural Network*

## Query Strategies 
* Max - Choose the most likely samples to be included according to the model
* Uncertainty - choose the most uncertain samples according to the model (i.e. closest to 0.5 probability) [@Lewis1994] 
* Random - randomly selects abstracts with no regard to model assigned probabilities. 
* Cluster - Use clustering after feature extraction on the dataset. Then the highest probabilities within random clusters are sampled

The following combinations are simulated:

* cluster
* max
* cluster * random 
* cluster * uncertainty
* max * cluster
* max * random
* max * uncertainty

## Balance Strategies

## Feature Extraction Strategies

# Combinations

@@

# References

### 2020-02-04 manuscript/index/index.Rmd
added definitions on model parameters - model (naive bayes) - feature selection - query strategy

# Introduction {.unnumbered}
ASReview takes the following parameters/arguments:

- a model
- a query strategy
- a balance strategy (fixed)
- a feature extraction strategy
- number of training data

The model is typically a learning algorithm used to predict the relevance of text. The following models will be compared:

* Naive Bayes (*nb*) [@Zhang2004]. 
*

>>>>

# Introduction {.unnumbered}
